Type Refinements for the Working Class

### 2015-11-09 paper.tex
wording

In other words, to know $\Refines{\Phi}{\phi}{\tau}$ (presupposing
$\RefinesCtx{\Phi}{\Upsilon}$) is to know, for any renaming of $\Upsilon$ to
$\Upsilon'$, which partial equivalence relation on the closed $\Upsilon'$-terms
of $\tau$ that $\phi$ denotes. At this point, it should be remarked that this
is very similar to the semantical explanation of typehood given in
\cite{martin-lof:1979}, except that we have generalized it to a multi-sorted
setting, and that we have fibred the entire apparatus over collections
$\Upsilon$ of symbols.

@@

When we have $\Refines{\cdot}{\phi}{\tau}$, we say that $\phi$ is an
\emph{global} refinement and may simply write $\GRefines{\phi}{\tau}$. By
weakening, if $\GRefines{\phi}{\tau}$ then for all $\Phi$, we have
$\Refines{\Phi}{\phi}{\tau}$ supposing $\RefinesCtx{\Phi}{\Upsilon}$.

>>>>

In other words, to know $\Refines{\Phi}{\phi}{\tau}$ (presupposing
$\RefinesCtx{\Phi}{\Upsilon}$) is to know, for any renaming of $\Upsilon$ to
$\Upsilon'$, which partial equivalence relation on the closed $\tau$-sorted
$\Upsilon'$-terms $\phi$ denotes. At this point, it should be remarked that
this is very similar to the semantical explanation of typehood given in
\cite{martin-lof:1979}, except that we have generalized it to a multi-sorted
setting, and that we have fibred the entire apparatus over collections
$\Upsilon$ of symbols.

@@

When we have $\Refines{\cdot}{\phi}{\tau}$, we say that $\phi$ \emph{globally}
refines $\tau$ and may simply write $\GRefines{\phi}{\tau}$. By weakening, if
$\GRefines{\phi}{\tau}$ then for all $\Phi$, we have
$\Refines{\Phi}{\phi}{\tau}$ supposing $\RefinesCtx{\Phi}{\Upsilon}$.
